Staged Compilation with Two-Level Type Theory

### 2022-07-30 paper/paper.tex
edit

In \cite{DBLP:conf/lics/Hofmann99}, it is described how to model higher-order
abstract syntax of simply typed object languages in presheaves over various
syntactic categories. In the case where syntactic morphisms are substitutions,
the internal language described by Hofmann can be viewed as an alternative
syntax for a 2LTT, where we only have a single family structure and the object
level is modeled with a Tarski-style universe.

>>>>

\cite{DBLP:conf/lics/Hofmann99} models higher-order abstract syntax of simply
typed object languages in presheaves over various syntactic categories. The main
difference between HOAS and 2LTT is that the former represents object-level binders
using meta-level functions while the latter has a primitive notion of object-level
binding.
